A Flexible Space-time Tradeoff on Hybrid Index with Bicriteria Optimization

### 2016-09-26 manuscript.tex
After submission, errors in font size is found in figure rcsp. Luckily it doesn't make too impact on reading. Now it has been corrected.

To facilitate both compression and query processing, posting lists from the index are always considered separate data stream, components in each posting lists (docid, frequency and position) are stored in a non-interleaved way, and the lists of docid and position are usually sorted and transformed to the corresponding sequence of differences(or \textit{gaps}) between adjacent values.
Hence, the task of index compression is best viewed code sequences of integers of the form $ x_{1},x_{2},x_{3},\ldots,x_{m} $ where $ x_{i}\geqslant0 $ for all $ 1\leqslant i\leqslant m $, and $ m $ is the number of the postings.

@@

$ \cal G $ is built as follows: a posting list can be treated as a list containing only positive integers $ L[0,m] $, where $ m $ is the number of postings.
Then each integer is represented by a vertex, plus a dummy vertex marking the end of the sequence.
$ \cal G $ is complete with $ O(m^2) $ edges, each edge is an exact correspondence of a partition in the $ L $.
The weight of an edge in the $ \cal G $ is equal to the cost in bits consumed by the partition.
The problem of fully partitioning $ L $ is converted to finding a path $\pi \in \Pi $ in $\mathcal{G}$, with its total edge weights $ \omega(\pi) $ minimized.

@@

Notice that in Equation~\eqref{equ: L(u,pi)} we have $ \mu \geqslant 0 $ and $ g(\pi) \leqslant 0 $, thus $ L(\mu,\pi) $ representing $ f(\pi) $ adding a negative number.
As we are trying to find a minimal $ f(\pi) $, we get the following equation:
\begin{equation}
L(\mu) \leqslant f(\pi^\star) \label{equ: maximum}
\end{equation}
\noindent For every $ \mu \geqslant 0 $.
Therefore, an best lower bound for the optimal path in RCSP can be found by solving its dual problem defined as 
\begin{equation}
L^\star = L(\mu^\star) = \max_{\mu \geqslant 0} L(\mu) =\max_{\mu \geqslant 0} \min_{\pi \in \Pi} \left[ f(\pi) + \mu g(\pi) \right]
\end{equation}

>>>>

To facilitate both compression and query processing, posting lists from the index are always considered separate data stream, components in each posting lists (docid, frequency and position) are stored in a non-interleaved way, and the lists of docid and position are usually sorted and transformed to the corresponding sequence of differences(or \textit{gaps}) between adjacent values.
Hence, the task of index compression is best viewed code sequences of integers of the form $ x_{1}, x_{2}, x_{3},\ldots, x_{m} $ where $ x_{i}\geqslant0 $ for all $ 1\leqslant i\leqslant m $, and $ m $ is the number of the postings.

@@

$ \cal G $ is built as follows: a posting list can be treated as a list containing only positive integers $ L[0, m] $, where $ m $ is the number of postings.
Then each integer is represented by a vertex, plus a dummy vertex marking the end of the sequence.
$ \cal G $ is complete with $ O(m^2) $ edges, each edge is an exact correspondence of a partition in the $ L $.
The weight of an edge in the $ \cal G $ is equal to the cost in bits consumed by the partition.
The problem of fully partitioning $ L $ is converted to finding a path $\pi \in \Pi $ in $\mathcal{G}$, with its total edge weights $ \omega(\pi) $ minimized.

@@

Notice that in Equation~\eqref{equ: L(u,pi)} we have $ \mu \geqslant 0 $ and $ g(\pi) \leqslant 0 $, thus $ L(\mu,\pi) $ representing $ f(\pi) $ adding a negative number.
As we are trying to find a minimal $ f(\pi) $, we get the following equation:
\begin{equation}
L(\mu) \leqslant f(\pi^\star) \label{equ: maximum}
\end{equation}
\noindent for every $ \mu \geqslant 0 $.
Therefore, an best lower bound for the optimal path in RCSP can be found by solving its dual problem defined as 
\begin{equation}
L^\star = L(\mu^\star) = \max_{\mu \geqslant 0} L(\mu) =\max_{\mu \geqslant 0} \min_{\pi \in \Pi} \left[ f(\pi) + \mu g(\pi) \right]
\end{equation}
